---
bibliography: includes/bib/lit-review.bib
classoption: report
documentclass: uncdissertation
fontsize: 12pt
output:
  pdf_document:
    includes:
      before_body: includes/tex/doc_prefix_unc.tex
      fig.caption: yes
      in_header: includes/tex/header-unc.tex
    keep_tex: yes
    number_sections: yes
    pandoc_args:
    - --filter
    - C:/Python38/Scripts/pandoc-eqnos.exe
  #   toc: no
  # word_document:
  #   toc: no
---


```{r include=FALSE}
#csl: includes/scripts/vancouver-authoryear.csl
#link-citations: yes

library(knitr)
library(kableExtra)
library(ggplot2)
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

<!-- NOTES: 

1. Some template code for formatting based on work from https://github.com/jvcasill/ua_thesis_rmd. All LaTeX code is copied from https://github.com/mmalahe/unc-dissertation including the .cls file.

2. Be careful of unicode characters, especially in the bibliography file. Very hard to find and can kick up errors that prevents the file from compiling. For example, a U+2AB unicode character that was not recognized and kept the program from compiling. or 'Package inputenc Error: Unicode char α (U+3B1)', which was actually in a journal title in the .bib file. Dashes are also problematic. See header-unc.tex to avoid that problem and add characters with 'declareunicodecharacters'.

Using pandoc-eqnos python program in pandoc to number equations:  https://github.com/tomduck/pandoc-eqnos
-->

<!-- Include introductory chapters. Also includes watermark text. -->

<!-- =========================== -->
<!-- START MAIN MATTER HERE -->
<!-- =========================== -->

\chapter{\uppercase{Inroduction}}
\addcontentsline{toc}{chapter}{\uppercase{Introduction}}


```{r, child='./sections/intro.Rmd', eval=T}
```


\chapter{\uppercase{Chapter 1: From intermittent to continuous water supply under increasing water prices - How does water demand change?}}
\addcontentsline{toc}{chapter}{\uppercase{Chapter 1: From intermittent to continuous water supply under increasing water prices - How does water demand change?}}


```{r, child='./sections/ms1.Rmd', eval=T}
```

<!-- Include tables and figures for first manuscript -->

```{r, child='includes/scripts/paper1/tables-figs.Rmd', eval=T}
```

\chapter{\uppercase{Chapter 2: What's in a Water Bill? Water bill payment behavior and service quality, prices, and household characteristics in Amravati, Maharashtra, India.}}
\addcontentsline{toc}{chapter}{\uppercase{Chapter 2: What's in a Water Bill? Water bill payment behavior and service quality, prices, and household characteristics in Amravati, Maharashtra, India.}}

```{r, child='./sections/ms2.Rmd', eval=T}
```

<!-- Include tables and figures for second manuscript -->

```{r, child='includes/scripts/paper2/tables-figs.Rmd', eval=T}
```

\chapter{\uppercase{Chapter 3: Intermittent to Continuous Water Supply: Implications for water demand, supply, revenue and long-term planning horizons in Amravati, Maharashtra, India.}}
\addcontentsline{toc}{chapter}{\uppercase{Chapter 3: Intermittent to Continuous Water Supply: Implications for water demand, supply, revenue and long-term planning horizons in Amravati, Maharashtra, India.}}

```{r, child='./sections/ms3.Rmd', eval=T}
```

<!-- Include tables and figures for third manuscript -->

```{r, child='includes/scripts/paper3/tables-figs.Rmd', eval=T}
```

\chapter{\uppercase{Conclusion}}
\addcontentsline{toc}{chapter}{\uppercase{Conclusion}}

```{r, child='./sections/conclusion.Rmd', eval=T}
```
<!-- Include references -->

\setlength{\parindent}{-0.2in}
\setlength{\leftskip}{0.2in}
\setlength{\parskip}{8pt}

\backmatter

<!-- Include appendices -->

\appendix

\chapter{\uppercase{Background for power calculations}}\label{app1}
\addcontentsline{toc}{chapter}{\uppercase{Appendix: Useful information}}

```{r, child='./sections/appendix.Rmd', eval=T}
```


\chapter*{REFERENCES}
\addcontentsline{toc}{chapter}{REFERENCES}
\printbibliography{}
